---
title: "Practical Machine Learning"
author: "Li Hui"
date: "Monday, November 23, 2015"
output: html_document
---
Summary: This data analysis is to predict the activity clasuse the lifting activity dataset 
```{r}
library(knitr)
setwd("E:/statistics/coursera/repository/practicalmachinelearning/project")
#The dataset has already been downloaded from the following website:"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", therefore I directly read it in.
training<-read.csv("pml-training.csv")
```

## look at the summary of the dataset, but do not show the the summary because it is too much and detailed.
```{r,results='hide'}
str(training)
```
The summary shows that there are a lot of NA values in the dataset. Therefore, the dataset will be preprocessed at first.

## If a column has 10% NA values, it will be depleted from the training dataset.
```{r, echo=TRUE,cache=TRUE}
ncol<-ncol(training)
nrow<-nrow(training)
index1<-numeric(length=ncol)
index2<-numeric(length=ncol)
for(i in 1:ncol){
    index1[i]<-0
    index2[i]<-0
    for(m in 1:nrow){
        if(is.na(training[m,i])){index1[i]<-index1[i]+1}
    }
}
for(n in 1:ncol){
    if(index1[n]>nrow*0.1){
     index2[n]<-n   
    }
}
index3<-index2[index2!=0]
processedtraining<-training[,-index3]
```

##Deplete the variables with little variance and the first index variable, the user variable and the time factor variable which are certainly not useful for prediction.
```{r,cache=TRUE}
library(caret)
nsv<-nearZeroVar(processedtraining,saveMetrics=TRUE)
nsvrow<-nrow(nsv)
index4<-numeric(length=nsvrow)
for(i in 1:nsvrow){
    if(nsv[i,4]){index4[i]<-i}
    else{index4[i]<-0}
}
index5<-index4[index4!=0]
processedtraining2<-processedtraining[,-c(1,2,5,index5)]
```

##Delete variables that is highly correlated
```{r}
M<-abs(cor(processedtraining2[,-56]))
diag(M)<-0
which(M>0.8,arr.ind=T)
processedtraining3<-processedtraining2[,-c(6,7,10,11,12,13,18,23,25,32,34,44,36,49)]
```

##Create training and testing dataset
```{r}
library(caret)
#My computer is limited while the dataset is a little large.Therefore I subset the rows from the processedtraining3 data.
subset<-sample(1:nrow(processedtraining3),0.05*nrow(processedtraining3),replace=FALSE)
training4<-processedtraining3[subset,]
set.seed(125)
inTrain<-createDataPartition(y=training4$classe,p=0.6,list=FALSE)
subsettrain<-training4[inTrain,]
subsettest<-training4[-inTrain,]
```

## Fit a model
```{r}
modelFit<-train(classe~.,data=subsettrain,method="rf",prox=TRUE)
confusionMatrix(predict(modelFit,subsettest),subsettest$classe)
```
The estimated out of sample error of this model is 0.9309.
